% Further certified margins.
% Sync note: stage-2 counts refer to the enlarged exclusion box.
% The 0.05 manifests were regenerated 2026-07-17 with exact B-matrix
% packets (leaf counts shifted 867 -> 855 and 1365 -> 1363 under the
% same policy, zero failures at every stage).  The -0.05 stage-2 and
% shoulder supplement were regenerated the same night with GRID_N
% recorded (1294 -> 1282 leaves; the supplement is new - the enlarged
% box's lattice needs it, and the first rerun's single shoulder leaf
% is preserved as evidence).  The remaining margins ship their
% original manifests.

\section{Further margins}
\label{sec:margins}

The four conditions of Theorem~\ref{thm:main} are margin-wise
statements, and the certificate pipeline of
Sections~\ref{sec:twovar}--\ref{sec:regionI} runs unchanged at any
$\kappa$ inside the strip where the fixed point is certified unique:
the pilot locates the $(q_0,\psi_0)$ boxes at both endpoints of the
$\alpha$ window, configures the exact-arithmetic modules from those
balls, and runs the same four pieces.  Beyond $\kappa=0.05$ we have
certified Condition~2varfn at $\kappa=-0.05$, where the fixed-point
uniqueness input comes entirely from the contraction certificates of
the companion strip (there is no independent derivation on the
negative side).  The certified pieces at both margins:

\begin{table}[h]
\centering
\small
\setlength{\tabcolsep}{4pt}
\begin{tabular}{lccccc}
\hline
$\kappa$ & $\alpha^*(\kappa)$ window & sweep & Region I & stage 2 &
inradius / required \\
\hline
$0.05$  & $[0.781073068,\ 0.781074776]$ & 855 & 1404 (+12) & 1363 &
$0.01481\ /\ 0.01209$ \\
$-0.45$ & $[1.557652103,\ 1.557654133]$ & 655 & 1404 (+12) & 1196 &
$0.01480\ /\ 0.01207$ \\
$-0.05$ & $[0.889408031,\ 0.889409783]$ & 884 & 1404 (+12) & 1282 &
$0.01527\ /\ 0.01209$ \\
$0.0995$ & $[0.733478513,\ 0.733480205]$ & 904 & 1404 (+12) & 1394 &
$0.01459\ /\ 0.01209$ \\
$0.13$  & $[0.705932217,\ 0.705933898]$ & 883 & 1404 (+12) & 1421 &
$0.01446\ /\ 0.01210$ \\
\hline
\end{tabular}
\caption{Certified leaf and band counts per piece, with zero failures
in every manifest.  Region~I counts marked $(+12)$ include the twelve
shoulder-supplement chunks; under the enlarged exclusion box every
margin's stage-2 lattice consumes one.  The final column gives the
constructive moment-body inradius against the required star radius,
both exact-arithmetic bounds.}
\end{table}

Every margin's Region-I manifest carries per-band interval packets
for the frozen-tilt matrix $B$, and the kernel-checked skeleton
includes for each a fifth family: Loewner definiteness of every
band's $B$-matrix, decided over the integers in thirteen chunks of
$108$ bands together with a decided total count ($55$ kernel theorems
per margin; the mutation battery rejects a sign corruption in each
family).

The $0.13$ run additionally exposed a completeness
defect in the stage-2 containment---supplement arcs stored on one
angular branch were invisible to cells whose interval fell on the
other, weakening containment only, never soundness---which was fixed
and the margin re-certified with zero failures.  One observation from
the $0.0995$ run is also methodologically relevant.  Its Region~II sweep initially
failed a single minimal-size cell just above the exclusion box's
upper edge, where the dual certificate degenerates in a thin ridge
(the certified value interval collapses to $[\pm 0.181]$ on a cell of
width $0.0018$, recovering two cell-widths higher).  The exclusion
box's upper offset moved from $+0.0961$ to $+0.1030$ in response;
this is sound without revisiting Region~I because the stage-2
containment derives its tiling from the same box and fails loudly if
the enlarged region outgrows what the star and supplement cover.  The
$0.05$ stage-2 was re-run against its published Region~I manifest
under the enlarged box on two machines independently; both certify
with 1365 leaves and zero failures, and the shipped manifest is the
box run with its bindings intact.

\input{interval_section}
